The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-14 paper.tex
Added to characterization section.

In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase shifters is known once it is built. However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production. One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} . However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can be as large as 900 modes (check citations for number of modes).

>>>>

In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase shifters is known once it is built. However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production. One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} . However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can now be as large as 900 modes (check citations for number of modes). Alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.

Generally, the unitary matrix of the $d\times d$ linear optical device are complex numbers $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$. The scheme in \cite{bib:Laing12} relies on injecting one-photon and two-photon states into the linear optical network with correlated photon detection. First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one-photon and two-photon data are insensitive to. This reduces the first row and first column elements to real numbers, i.e. $\theta_{1j}=\theta_{i1}=0$. Second, the photon statistics remain unchanged under the complex conjugation of $U$. Thus, the imaginary part of $M_{2,2}$ must be non-negative.
